cardinalR: Generating interesting high-dimensional data structures

### 2025-04-30 paper-cardinalR.Rmd
Added sphere_tb

```{r}
sphere_tb <- tibble(fun = c("gen_circle",
                            "gen_curvycycle",
                            "gen_unifsphere",
                            "gen_gridedsphere",
                            "gen_clusteredspheres"), 
                        exp = c("",
                                "",
                                "",
                                "",
                                ""))
```

>>>>

```{r}
sphere_tb <- tibble(fun = c("gen_circle",
                            "gen_curvycycle",
                            "gen_unifsphere",
                            "gen_gridedsphere",
                            "gen_clusteredspheres",
                            "gen_hemisphere"), 
                        exp = c("Generate a circle.",
                                "Generate a curvy cell cycle.",
                                "Generate a uniform sphere.",
                                "Generate a grided sphere.",
                                "Generate multiple small spheres within a big sphere.",
                                "Generate a hemisphere."))
```
